### 2018-05-19 Sections/protocols_for_the_quantum_internet.tex
Minor, superdense coding, authors

\textit{Superdense coding} is a communications protocol, which utilises shared entanglement between two parties to increase the rate at which classical information may be transmitted between them.

>>>>

\textit{Superdense coding} is a hybrid quantum/classical communications protocol for increasing classical bit-rates between two parties, who share entanglement as a resource.
